### 2008-03-15 SAiP/Module1/H3/doc/architecturaldescription.tex
Adding beginning of SOA

\fixme{Answer question 2.2}

@@

\fixme{Answer question 2.4}

>>>>

\fixme{Finish question 2.2}

@@

In a sense there are already aspects of SOA in the architecture, as the validation of the credit card information is most likely performed using a service on the internet - not that web services and SOA is equivalent, but they do complement each other nicely.

As SOA consists of a collection of (preferrably stateless) well-defined services what needs to be desctibed is, which existing (external) services are needed and which new services has to be created. This may be done using the MacKenzie Topic maps, which describe the static dependencies between the services.

The static description is naturally not sufficient, and two other views may be presented to show the Dynamic interrelations; Visibility and Interaction.

\fixme{Finish question 2.4}
